\documentclass[9pt]{style/developercv}

\edef \myLocation{\directlua{tex.sprint(os.getenv('LOCATION'))}}
\edef \myCellPhone{\directlua{tex.sprint(os.getenv('CELL_NUMBER'))}}
\edef \myEmailLink{\directlua{tex.sprint(os.getenv('EMAIL_LINK'))}}
\edef \myEmail{\directlua{tex.sprint(os.getenv('EMAIL_DISPLAY'))}}
\edef \myWebsiteLink{\directlua{tex.sprint(os.getenv('WEBSITE_LINK'))}}
\edef \myWebsite{\directlua{tex.sprint(os.getenv('WEBSITE_DISPLAY'))}}
\edef \myLinkedinLink{\directlua{tex.sprint(os.getenv('LINKEDIN_LINK'))}}
\edef \myLinkedin{\directlua{tex.sprint(os.getenv('LINKEDIN_DISPLAY'))}}

\hypersetup{
	pdfinfo={
	Title={Gondek: Curriculum Vitae},
	Subject={Gondek: Curriculum Vitae},
	Keywords={
		Containers, Kubernetes, Python, 
		Nix, Nixpkgs, NixOS, 
		Scala, Microservices, Functional Programming,
		Bazel, Argo, NoSQL,
		Actor Model Framework,
	},
	Author={Aleksander Gondek}
}}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip}

	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Aleksander}}}}}
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Gondek}}}}}
	
	\vspace{6pt}
	
	{\huge Software Engineer}
\end{minipage}
\begin{minipage}[t]{0.275\textwidth}
	\vspace{-\baselineskip}
	
	\icon{MapMarker}{12}{\myLocation}\\
	\icon{Phone}{12}{\myCellPhone} \\
	\icon{At}{12}{\href{\myEmailLink}{\myEmail}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth}
	\vspace{-\baselineskip}
	
	\icon{Globe}{12}{\href{\myWebsiteLink}{\myWebsite}}\\
	\icon{Github}{12}{\href{https://github.com/AleksanderGondek}{AleksanderGondek}}\\
	\icon{Linkedin}{12}{\href{\myLinkedinLink}{\myLinkedin}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	Jack of all trades, master of at least one - having a broad software development experience 
	and deep passion for work, I seek to bring state-of-art solutions to any endeavour
	I have currently embarked upon. \\ \\
	Above all, I enjoy working with complex systems and simplifying them in the process.

\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{Python}{80}
		\baritem{Bazel}{75}
		\baritem{Kubernetes}{70}
		\baritem{Nix}{60}
		\baritem{Scala}{50}
		\baritem{Microservices}{70}
	\end{barchart}
\end{minipage}

\vspace{1cm}

%----------------------------------------------------------------------------------------
%	TOP QUALITIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}

	\cvsect{Craftmanship}

	As a firm supporter of \href{https://manifesto.softwarecraftmanship.org/}{Software craftmanship manifesto},
	I took pride in my work and always strive to deliver solutions which are not only functional, 
	but well-crafted and well thought-out. I am known for implementing solutions built to last.

\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	
	\cvsect{Ownership}
	
	When given a task, project or issue to solve, I always take full responsibility for the outcome - doing my upmost
	best to deliver solution that is tailor-suited for the occasion, whilst fostering cooperative approach in development
	process, often times breaking well-established silos.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	
	\cvsect{Creativity}
	
	Throughout my career, I have been frequently recognized as person who challenges status quo and implements disruptive
	improvements to existing processes. I have a track record of resolving various issues in innovative manner. 
\end{minipage}

\vspace{0.75cm}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
	  {May 2021 -- Present\\\footnotesize{Software Engineer}}
		{Software Developer Productivity Engineer}
		{Tweag.io}
		{
			\texttt{Nix}\slashsep
			\texttt{Bazel}\slashsep
			\texttt{Python}\slashsep
			\texttt{Cpp}\slashsep
			\texttt{Rust}\\

			Migrated large monorepository encompassing Cpp \& Python to Bazel.
			Dropped builds \& tests times from hours to minutes, started working on introduction of Remote Execution.
	  }
	\entry
	  {Sep 2020 -- May 2021 \\\footnotesize{Software Engineer}}
		{Kubernetes Platform Engineer}
		{Dynatrace}
		{
			\texttt{Python}\slashsep
			\texttt{Nix}\slashsep
			\texttt{Kubernetes}\slashsep
			\texttt{Bazel}\slashsep
			\texttt{Cuelang}\slashsep
			\texttt{Rancher}\slashsep
			\texttt{AKS/EKS}\\

			Leading the development of Dynatrace deployment systems and processes targeting Kubernetes in
			multiple flavours: AKS, EKS, GKE, Openshift, on prem.
	  }
	\entry
	  {Mar 2020 -- Sep 2020\\\footnotesize{Software Engineer}}
		{Platform Research Engineer}
		{Dynatrace}
		{
			\texttt{Python}\slashsep
			\texttt{Nix}\slashsep
			\texttt{Azure}\slashsep
			\texttt{AWS}\\

			Researched new valuable integrations to be added to Dynatrace platform. 
			Main area of impact made: scaffolding tool for preparing integration with any
			Azure / AWS service.
	  }
	\entry
		{Nov 2019 -- Mar 2020\\\footnotesize{IT Expert Developer}
		\\Nov 2018 -- Nov 2019\\\footnotesize{Senior IT Developer}}
		{Scala Tech Lead (DevOps Developer)}
		{Nordea}
		{
			\texttt{Scala}\slashsep
			\texttt{Nix}\slashsep
			\texttt{Kubernetes}\slashsep
			\texttt{Bazel}\slashsep
			\texttt{Argo}\slashsep
			\texttt{Elastic Search}\slashsep
			\texttt{Kafka}\\

			Developing proprietary solution akin to 
			\href{https://egeria.odpi.org}{Egeria}, based upon microservices 
			architecture and realising high availability demands. The solution
			allows users to search and exchange different metadata used by wide
			range of internal teams.\\ \\
			Most notably, I was responsible for planning and implementation of 
			ecosystem redesign, which improved cross-systems integrations and 
			solution flexibility. Due to changes made, the crucial ability of 
			the project to adjust to ever-changing landscape of Data Lake was
			reduce significantly (dropped from months to days). \\
		}
	\entry
		{Apr 2018 -- Nov 2018\\\footnotesize{IT Infrastructure Specialist}}
		{Container Platform Engineer}
		{Nordea}
		{
			\texttt{Ansible}\slashsep
			\texttt{Python}\slashsep
			\texttt{Kubernetes}\slashsep
			\texttt{Rancher}\slashsep
			\texttt{OpenShift}\slashsep
			\texttt{Grafana}\\

			I have created the PoC of container-based application platform, build 
			from the ground up with automation, policy enforcement, 
			openness and configurability in mind. 
			It has been constructed from exclusively open-source components to
			allow for maximum synergy with current cloud-base 
			tools and practices. \\
			PoC received very good initial feedback from the developers, 
			who found out it significantly simplified their every-day work.\\ \\
			Most notably, the platform allowed multiple teams within the company
			to increase their work velocity and take ownership of their full technological
			stack.
		}
	\entry
		{Mar 2015 -- Apr 2018\\\footnotesize{Graphics Software Engineer}}
		{Full Stack Developer}
		{Intel Corporation Poland}
		{
			\texttt{Python}\slashsep
			\texttt{Flask}\slashsep
			\texttt{Celery}\slashsep
			\texttt{Docker}\slashsep
			\texttt{Riak}\slashsep
			\texttt{AngularJS 1}\slashsep
			\texttt{Redis}\\

			I was part of team developing internal test management and reporting 
			system which processed significant amounts of data daily, giving 
			the end-user ability to perform flexible, customizable lookups
			and follow latest data trends.
			Solution was built with micro-services oriented architecture, with 
			focus being placed on high availability and scalability.
			Working in fully cross-functional manner allowed me to deliver 
			improvements in infrastructure, web, backend and database layers 
			of the system.\\ \\
			The key accomplishment was the redesign of how system messages are 
			handled, which improved overall solution performance and adaptability to
			change.
		}
	\entry
		{Mar 2014 -- Mar 2015\\\footnotesize{Internship}}
		{C\# Developer}
		{Intel Corporation Poland}
		{
			\texttt{ASP.NET}\slashsep
			\texttt{JS}\slashsep
			\texttt{MS-SQL}\slashsep
			\texttt{.NET MVC}\slashsep
			\texttt{Workflows}\\

			Single-handedly revamped automation/workflow solution which integrated
			multiple internal proprietary tools, needed for processing changes to 
			graphical driver. As a result, time-to-delivery of driver patches was 
			decreased, and I was awarded with Department Recognition Award.
		}
	\entry
		{Jul 2013 -- Aug 2013\\\footnotesize{Internship}}
		{Android Application Tester}
		{SolDevelo}
		{
			\texttt{Java}\slashsep
			\texttt{Android}\slashsep
			\texttt{Spring}\slashsep
			\texttt{Validation}\slashsep
			\texttt{Continuous Integration}\\

			I was part of the validation team responsible for testing whether 
			mobile app meets the user expectations and covers all gathered user 
			stories. Since the app was written in  Java for Android, all testing 
			was also done in Java. Most of the skills acquired relate to proper 
			testing and systems integration.
		}
	\entry
		{Sep 2011 -- Mar 2014\\\footnotesize{Freelance}}
		{Web Developer}
		{}
		{
			\texttt{JS}\slashsep
			\texttt{CSS}\slashsep
			\texttt{Bootstrap}\slashsep
			\texttt{.NET MVC}\slashsep
			\texttt{Node.js}\\
		}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2014 -- 2016}
		{Master of Engineering, Computer Science}
		{Gdańsk University of Technology}
		{
			Specialization: Distributed Applications and Internet Services \\
			Studies were conducted in English language
		}
	\entry
		{2010 -- 2014}
		{Bachelor of Engineering, Computer Science}
		{Gdańsk University of Technology}
		{}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}

	\cvsect{Languages}

	\textbf{English} - proficient\\
	\textbf{German} - rudimentary\\
	\textbf{Polish} - native
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	
	\cvsect{Hobbies}
	
	Role-playing games\\
	Speculative fiction\\
	Cinematography\\
	Distributed systems
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	
	\cvsect{Certificates}
	
	Cambridge English: Proficiency
	Functional Program Design (\textit{EPFL})\\
	Functional Programming Principles (\textit{EPFL})
\end{minipage}

%----------------------------------------------------------------------------------------

\vspace{1.00cm}

\begin{minipage}[t]{1\textwidth}
	\footnotesize{I hereby agree to the processing of personal data provided in this document for 
	realising the recruitment process pursuant to the Personal Data Protection Act
	of 10 May 2018 (Journal of Laws 2018, item 1000) and in agreement with Regulation (EU) 
	2016/679 of the European Parliament and of the Council of 27 April 2016 on the 
	protection of natural persons with regard to the processing of personal data and on 
	the free movement of such data, and repealing Directive 95/46/EC (General Data 
	Protection Regulation).}
\end{minipage}

\end{document}
